\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex
add a sentence to sec2

Although \code{mark-hit} will operate on sensitive data (the game
boards), it is written without any special machinery to maintain the
secrecy of \code{board}. Protecting data {w.r.t.} policies is instead handled
automatically and implicitly by a runtime monitor.
When Alice and Bob want to play a game, they both create a
\emph{label} to protect their data. A label is unique id mapped to a policy predicate
that takes an key (e.g., the current user's name) and returns true or false to indicate
permission for the label. Alice's label is used to annotate data she wants
to be kept secret. Supposing Alice chooses to be player 1, she may use the
following label:

@@

In the above example, \blue{$\star$} (lazy failure) is used in the negative branch
to ensure execution will fail if Bob tries to observe Alice's secret gameboard.
The $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ \blue{e_\text{fac}}\code{)}$ form takes
a label, a key, and a faceted value. Explicit observation projects a single label
$\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ to either its positive or negative facet,
depending on whether the policy associated with $\blue{e_\ell}$ returns true for key
$\blue{e_\text{key}}$. If Bob tries to observe Alice's board, the policy predicate
will return false (from \texttt{(= 1 $\blue{2}$)}) and Alice's negative facet $\blue{\star}$ will result.

>>>>

Although \code{mark-hit} will operate on sensitive data (the game
boards), it is written without any special machinery to maintain the
secrecy of \code{board}. Protecting data {w.r.t.} policies is instead handled
automatically and implicitly by a runtime monitor.
When Alice and Bob want to play a game, they both create a
\emph{label} to protect their data. A label is unique id mapped to a policy predicate
that takes a key (e.g., the current user's name) and returns true or false to indicate
permission for the label. Alice's label is used to annotate the data she wants
to be kept secret. Supposing Alice chooses to be player 1, she may use the
following label:

@@

In the above example, \blue{$\star$} (lazy failure) is used in the negative branch
to ensure execution will fail if Bob tries to observe Alice's secret gameboard. To observe
Alice's gameboard, Bob can try to use $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ 
\blue{e_\text{fac}}\code{)}$ form, which takes a label, a key, and a faceted value.
Explicit observation projects a single label $\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ 
to either its positive or negative facet, depending on whether the policy associated 
with $\blue{e_\ell}$ returns true for key $\blue{e_\text{key}}$. If Bob tries to observe 
Alice's board, the policy predicate will return false (from \texttt{(= 1 $\blue{2}$)}) 
and Alice's negative facet $\blue{\star}$ will result.
